Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-01-15 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
Minor details
add Cache for chunks, autodep for Chunk 8

```{r setup, include=FALSE}
#knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

@@

if(!require("rstudioapi")) install("rstudioapi")
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

@@

* \cite{correa1995new}: $\widehat{H}_{\text{C}}$.

* \cite{Ebrahimi1994}: $\widehat{H}_{\mathrm{E}}$.

* \cite{IbrahimAlOmari2014}: $\widehat{H}_{\mathrm{AO}}$.

@@

```{r Simulated_density, echo=FALSE, message=FALSE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

all_summary_stats <- list()
all_TestStatistics <- list()
all_TestNormality <- list()
all_plots <- list()

@@

    # Almacenar resultados de normalidad
    # summary_normality <- rbind(summary_normality, data.frame(LValue = as.character(L),
    #                                                          SampleSize = s,
    #                                                          lilliepvalue = lillie_p_value,
    #                                                          adpvalue = ad_p_value))
  }

@@

#save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
  save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
}

@@

# for (L in L_values) {
#   summary_stats <- all_summary_stats[[as.character(L)]]
#   
#   print(summary_stats)
# }

# summary_stats_2 <- all_summary_stats[["2"]]

@@

# Cargar los resultados guardados
load("./Data/results_2.Rdata")
load("./Data/results_5.Rdata")
load("./Data/results_8.Rdata")
load("./Data/results_18.Rdata")

# Tamaño de muestra específico que deseas graficar
selected_sample_size <- 100

# Crear una lista para almacenar los ggplots
ggplot_list <- list()

# Para cada valor de L
for (L in c(2, 5, 8, 18)) {
  TestStatistics1 <- all_TestStatistics[[as.character(L)]]

  # Verifica si el tamaño de muestra seleccionado está disponible
  if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
    p <- ggplot(TestStatistics1[[as.character(selected_sample_size)]], 
                aes(sample = Test_Statistics)) +
      geom_qq(col = "blue", shape = 20) +
      geom_qq_line(col = "darkgreen", linetype = 2) +
      labs(title = bquote(italic(L) == .(L)),
           x = "Theoretical Quantiles",
           y = "Sample Quantiles") +
      theme(plot.title = element_text(hjust = 0.5))#titulo centrado

@@

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache=TRUE)
#knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(reshape2)
#library(plotly)
library(knitr)
library(pandoc)
library(gridExtra)
library(gtools)
library(stats4)
library(rmutil)
library(scales)
library(tidyr)
library(rmutil)
library(invgamma)
library(tidyverse)
library(RColorBrewer)
library(ggsci)
#library(wesanderson)
library(ggpubr)
library(patchwork)
library(dplyr)
#options(kableExtra.latex.load_packages = FALSE)
library(devtools)
#devtools::install_github("haozhu233/kableExtra")
library(kableExtra)
library(ggthemes)
library(latex2exp)
library(e1071)# kurtosis
library(viridis)
library(nortest)# AD

@@

# if(!require("rstudioapi")) install("rstudioapi")
# setwd(dirname(rstudioapi::getActiveDocumentContext()$path))

@@

* Correa&nbsp;\cite{correa1995new}: $\widehat{H}_{\text{C}}$.

* Ebrahimi et al&nbsp;\cite{Ebrahimi1994}: $\widehat{H}_{\mathrm{E}}$.

* Al Omary&nbsp;\cite{IbrahimAlOmari2014}: $\widehat{H}_{\mathrm{AO}}$.

@@

```{r Simulated_density, echo=FALSE, message=FALSE, cache = TRUE, autodep = TRUE}
set.seed(1234567890, kind = "Mersenne-Twister")

@@

all_summary_stats <- list()
all_TestStatistics <- list()
#all_TestNormality <- list()
#all_plots <- list()

@@

    # summary_normality <- rbind(summary_normality, data.frame(LValue = as.character(L),
    #                                                          SampleSize = s,
    #                                                          lilliepvalue = lillie_p_value,
    #                                                          adpvalue = ad_p_value))
  }

@@

#save(all_TestStatistics, all_summary_stats, all_TestNormality, file = paste0("./Data/results_", L, ".Rdata"))
  save(all_TestStatistics, all_summary_stats, file = paste0("./Data/results_", L, ".Rdata"))
}

@@

@@

# Load saved results
load("./Data/results_2.Rdata")
load("./Data/results_5.Rdata")
load("./Data/results_8.Rdata")
load("./Data/results_18.Rdata")

# Specific sample size
selected_sample_size <- 100

# 
ggplot_list <- list()

#  L
for (L in c(2, 5, 8, 18)) {
  TestStatistics1 <- all_TestStatistics[[as.character(L)]]

  # 
  if (as.character(selected_sample_size) %in% names(TestStatistics1)) {
    p <- ggplot(TestStatistics1[[as.character(selected_sample_size)]], 
                aes(sample = Test_Statistics)) +
      geom_qq(col = "blue", shape = 20) +
      geom_qq_line(col = "darkgreen", linetype = 2) +
      labs(title = bquote(italic(L) == .(L)),
           x = "Theoretical Quantiles",
           y = "Sample Quantiles") +
      theme(plot.title = element_text(hjust = 0.5))#titulo centrado

@@

  plot <- ggplot(TestStatistics1, aes(x = Test_Statistics)) +
    geom_line(aes(col = factor(Sample_Size), linetype = factor(Sample_Size)), stat = "density", linewidth = 1.0) +
    geom_line(data = TestStatistics2, aes(x = Test_Statistics2), stat = "density", color = "blue", linetype = "dashed", linewidth = 1) +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    annotate("text", x=difference.betweeen.GammaSAR.GI0.n.Look(-8, 5), y=7, parse=TRUE, label="alpha==-8", hjust=-.1, vjust=1.0, col="darkgreen") +
    geom_vline(xintercept = difference.betweeen.GammaSAR.GI0.n.Look(-1000, 5), col="darkgreen", linetype = "dotted", linewidth = 0.6) +
    theme_minimal() +
    theme(
      text = element_text(family = "serif"),
      legend.position = "none"  
    )+
    labs(x = "Test Statistics", y = "Density")
